Unsupervised embeddings capture latent structure of scientific mobility

### 2020-02-28 paper/current/main.tex
add_sentense_to_semaxis_result

In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility. 
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$). 
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
This suggests that word embeddings, in addition to learning the latent geography of mobility, also capture more nuanced characteristics such as latent hierarchy.

@@

By learning a distance directly from the data, the \SGNS{} model effectively and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing. 
This methodology is broadly applicable to studies of mobility.
Its success also points to the broad applicability of ideas from language and graph embedding techniques such as GLoVE~\autocite{pennington2014glove}, BERT~\autocite{devlin2018bert}, hyperbolic embeddings~\autocite{nickel2017poincare, linzhuo2020hyperbolic}, and persona2vec () to other problem domains, such as the social sciences. 
In addition to their technical advantages and the unique suite of methodologies they allow, they are also  readily transferable and can be trivially fit into a diverse array of analyses.

>>>>

In addition to learning geography, its clear that the \SGNS{} model is also encoding the latent prestige hierarchies of academic mobility. 
To test this, we derive a ranking using the prestige axis that we call \textit{SemRank}, and compare them to traditional university rankings. 
SemRank is defined from the position of organizations along the prestige axis, with the top ranked being the furthest towards the \textit{Elite} end of the axis.
We find that SemRank derived is highly correlated with the Times ranking ($\rho = 0.81$, Fig.~\ref{fig:semaxis}b). 
This correlation is robust with the number of organizations used to define the axes (Fig. SI~\ref{fig:supp:semaxis_compare}), such that even using only the single top-ranked and bottom-ranked universities is strongly correlated with the Times Ranking ($\rho = 0.46$). 
For reference, SemRank achieves correlation with the Times Ranking comparable to that between the Times ranking and the Leiden Ranking mean-normalized citation score ($\rho = 0.87$). 
This suggests that \SGNS{} model, in addition to learning the latent geography of mobility, while capture more nuanced characteristics such as latent hierarchy in the axis of the embedding, which is fascinating characteristic of our approach.

@@

By learning a distance directly from the data, the \SGNS{} model successfully  and efficiently captures a robust measure of semantic distance between entities, all with existing tools and minor data processing. 
This methodology is broadly applicable to studies of mobility.
Its success also points to the broad applicability of ideas from language and graph embedding techniques such as GLoVE~\autocite{pennington2014glove}, BERT~\autocite{devlin2018bert}, hyperbolic embeddings~\autocite{nickel2017poincare, linzhuo2020hyperbolic}, and persona2vec () to other problem domains, such as the social sciences. 
In addition to their technical advantages and the unique suite of methodologies they allow, they are also  readily transferable and can be trivially fit into a diverse array of analyses.
